### 2023-04-12 Documentation/UFMG/PFCII/Capa/capa.tex
documentation

    \begin{figure}
            \centering
            % \subfigure{\includegraphics[width=5cm]{Figuras/wac.png}}
            \hspace{0.1\textwidth}
            \subfigure{\includegraphics[width=6cm]{Figuras/nhl-stenden.png}}
            \vspace{3cm} 
        \end{figure}

    {\bf\Large EHDA closed loop control system based on real time non-visual spray mode classification\\}
    \vspace{1cm} 
    {\Large Monography}
    \vspace{2cm}

@@

>>>>

    \vspace{2cm}
    \begin{figure}[h]
        \centering
        \includegraphics[scale=0.5]{Figuras/brasao_ufmg.png}
    \end{figure}
    \vspace{2cm}

    {\bf\Large EHDA closed loop control system based on real time non-visual spray mode classification\\}
    \vspace{2cm} 
    {\Large Monography}
    \vspace{2cm}

@@

    \newpage
\clearpage
\thispagestyle{empty}

\begin{titlepage}

\centering
\vspace{2cm}
\textbf{Monography}\\
\vspace{2cm}
\centering
\textbf{EHDA closed loop control system based on real time non-visual spray mode classification.}\\
\vspace{5cm}

\parbox{1.0\textwidth} 
{\large 
Document submitted to the examining board designated by the Lectoraat Watertechnology at the NHL Stenden University of Applied Sciences and the Colegiado de Engenharia de Controle e Automação at the Universidade Federal de Minas Gerais as part of the requirements for approval in the subject Final Course Project II.}

\vspace{7cm}

### 2023-04-12 Documentation/UFMG/PFCII/Introduction/Introduction.tex
documentation

\section{Motivation and Justify}
\label{sec:motivacao}
% Argumente sobre a importância do projeto desenvolvido usando uma visão de alto nível, sem entrar em detalhes. Contextualize seu projeto dentro do local de execução ou da literatura e explique como ele é necessário ou inovador. É possível fazer uma breve revisão bibliográfica, confrontando seu trabalho com outras referências bibliográficas para mostrar a sua contribuição. No quesito contribuição, é muito importante deixar claro o tempo todo que partes do projetos foram executadas por outros e que partes foram executadas por você. Caso contrário, corre-se o risco de inadvertidademente tomar crédito pelo trabalho de outrem, o que pode ter implicações legais.

@@

As pesquisas de EHDA têm contribuído como uma importante ferramenta para
o desenvolvimento da tecnologia . Embora existam aplicações de EHDA em
indústria, a estabilização do modo de pulverização de jato cônico é feita empiricamente e com base em medições de corrente média.
A corrente elétrica que flui transportada pelo spray revela formas características para diferentes modos de atomização.
Essas formas não podem ser simplesmente resumidas por seu valor médio. Na figura um podemos ver um exemplo de cone-jet
modo eletrospray.

Figura 1: exemplo de EHDA

As técnicas de processamento de sinal podem permitir uma classificação não visual do modo de pulverização com base no elétrico
forma atual. O processo de pulverização impõe ruídos e sequências aleatórias no sinal medido tornando-o
classificação não é uma tarefa trivial.
Aplicações industriais exigem estabilização automatizada de um modo de pulverização. Isso pode ser obtido por um sistema fechado
sistema de controle de circuito. A classificação automatizada do modo de pulverização é uma parte crucial de um sistema de controle, assim como
o desenvolvimento de um algoritmo de controle apropriado.

\section{Project Goals}
\label{sec:objetivos}

Tendo em vista o exposto acima, este projeto tem por objetivos:

multipurpose applications
both scientific and industrial application

\begin{enumerate}[a)]
\item Fully automated and intuitive system for EHDA research and industrial application.
\item Real Time non-visual classification.    
\item Control and stabilization of desired spraying modes.   
\item System Portability.
\end{enumerate}

O conteúdo desta seção pode se sobrepor um pouco com o da seção anterior, podendo ela ser um sumário dos pontos expostos anteriormente. A escolha do título da seção talvez seja mais apropriada para a fase de proposta do projeto. Afinal, nesta fase se conhecem os objetivos e não os resultados. Por outro lado, fará pouco sentido discutir objetivos quando o projeto está finalizado, especialmente se tais objetivos não foram alcançados.

\section{People envolved}
\label{sec:empresa}

% Faça uma breve apresentação da empresa ou laboratório onde o projeto é desenvolvido. Fale um pouco da história da empresa, do mercado em que atua, da sua organização, do departamento em que está inserido o projeto, etc. Descreva também o seu vínculo com a empresa. 
Implementações de processamento de sinal de projetos anteriores
do grupo NHL Stenden Water Technology estão mostrando bons resultados de classificação. Mais pesquisas são
necessário para melhorar a precisão da classificação e pesquisa e implementação de uma classificação adequada
algoritmo. Por causa disso, o trabalho será feito pelo Water Technology Group da NHL Stenden University
de Ciências Aplicadas e em combinação com empresas holandesas para combinar possibilidades de análise com conhecimento
e disponibilidade de infraestrutura.

>>>>

\section{Motivation and Justify}
\label{sec:motivacao}

% Argumente sobre a importância do projeto desenvolvido usando uma visão de alto nível, sem entrar em detalhes. Contextualize seu projeto dentro do local de execução ou da literatura e explique como ele é necessário ou inovador. É possível fazer uma breve revisão bibliográfica, confrontando seu trabalho com outras referências bibliográficas para mostrar a sua contribuição. No quesito contribuição, é muito importante deixar claro o tempo todo que partes do projetos foram executadas por outros e que partes foram executadas por você. Caso contrário, corre-se o risco de inadvertidademente tomar crédito pelo trabalho de outrem, o que pode ter implicações legais.

@@

EHDA research has contributed as an important tool for the development of technology. 
Although there are applications of EHDA in industry, the stabilization of the conical jet spray mode is done empirically and based on average current measurements.
The flowing electrical current carried by the spray reveals characteristic shapes for different atomization modes.
These forms cannot simply be summarized by their average value. In figure one we can see an example of cone-jet electrospray mode.

Figure 1: example of EHDA

Signal processing techniques may allow non-visual classification of spray mode based on electrical current form. 
The spraying process imposes noise and random sequences on the measured signal making it sorting is not a trivial task.
Industrial applications require automated stabilization of a spray mode. 
This can be achieved by a closed system loop control system. 
Automated spray mode sorting is a crucial part of a control system, as well as the development of an appropriate control algorithm.

\section{Project Goals}
\label{sec:goals}

In view of the above, this project aims to:

\begin{enumerate}[a)]
\item multipurpose applications both scientific and industrial application.
\item Fully automated and intuitive system for EHDA research and industrial application.
\item Real Time non-visual classification.    
\item Control and stabilization of desired spraying modes.   
\item System Portability.
\end{enumerate}

% The content of this section may overlap somewhat with that of the previous section, and it may be a summary of the points made above. 
% The choice of section title may be more appropriate for the project proposal phase. 
% After all, at this stage the objectives are known and not the results. 
% On the other hand, it makes little sense to discuss objectives when the project is finished, especially if those objectives have not been achieved.

\section{People envolved}
\label{sec:companies}

% Faça uma breve apresentação da empresa ou laboratório onde o projeto é desenvolvido. Fale um pouco da história da empresa, do mercado em que atua, da sua organização, do departamento em que está inserido o projeto, etc. Descreva também o seu vínculo com a empresa.

Signal processing implementations from previous projects from the NHL Stenden Water Technology group are showing good ranking results. 
More research is necessary to improve classification accuracy and research and implementation of proper classification algorithm. 
Because of this, the work will be done by the Water Technology Group at NHL Stenden University of Applied Sciences and in combination with Dutch companies to combine analysis possibilities with knowledge and availability of infrastructure.

### 2023-04-12 Documentation/UFMG/PFCII/Metodology/Metodology.tex
documentation

This chapter is about describing the metodology and developments to achieve the project goals. 
The python routine which this project is about was developed by the previous student working on it.\cite{Monica}
The works therefore presented here are a continuation and optimization of the routine to make it more precise and applicable to industries application or research.

From the optimizations made, it highlights the following:

- Integrate high speed camera to the experiment routine.

- Remodel the software to support threads in order to separate the sensoring and controlling routines.

- Reduce the data collected size.

- Synchronize the power supply step commands and voltage sensoring.

- Reestructure the setup file in order to make it more intuitive to use the experiment.

- Improvements in code organization and readability.

@@

    \begin{figure}[H]
        \center
        \includegraphics[width=13cm]{Figuras/ganan_calvo_map.png}
        \caption{Domains of existence (stability) of Taylor cone-jets. \cite{gananCalvo} }
        \label{fig:ganan_calvo_fig}
    \end{figure}

@@

    In the figures 5 and 6 we can see the results of this mapping experiments. The liquid used is pure ethanol. 
    Each figure has 3 graphs with shared x axis representing the samples collected. The first is the current values collected through all the experiment.
    The second is the voltage values applied in each window of data collected. The colors represent the spraying classification defined by our routine.
    The third graph shows the current mean value of each data sample.
    Note that the experiment is composed of loops that increase voltage, change flowrate and repeat.

    \begin{figure}[H]
        \center
        \includegraphics[width=15cm]{Figuras/report2/map2Data.png}
        \caption{Mapping Experiment example 1}
        \label{fig:map2Data_fig}
    \end{figure}

    \begin{figure}[H]
        \center
        \includegraphics[width=15cm]{Figuras/report4/map-2023-03-02.png}
        \caption{Mapping Experiment example 1}
        \label{fig:map3Data_fig}
    \end{figure}

>>>>

This chapter is about describing the metodology and developments to achieve the project goals. 
The python routine which this project is about was developed by the previous student that worked on it.\cite{Monica}
The works therefore presented here are a continuation and optimization of the routine to make it more precise and applicable to both industrial and research approaches.

About the activities made to reach our goals, it highlights the following:

- Integrate high speed camera and liquid pump to the peripherals connected to the software.

- Develop of a control model to automatic stabilize the electrospraying mode.

- Remodel the software to support threads in order to separate each subsystem and exchange data beetween them with use of queues data structures.

- Reduce the data collected size and optimize the saving to a real time streamming.

- Develop new automatic experiment routines such as mapping and control routines.

- Reestructure the setup file and the algorithm usability in order to make it more intuitive.

- Integration with many computer architectures to be able to run in a portable computer such as a \emph{Raspberry Pi}.

@@

During the cone-jet, multiple parameters and variables influence the current, flow rate and voltage operational window. The operational window, seen in Figure \ref{fig:ganan_calvo_fig} can be defined where the cone jet spraying mode can be stabilized based on the flow rate, voltage and the setup configuration\cite{gananCalvo}.

    \begin{figure}[H]
        \center
        \includegraphics[width=13cm]{Figuras/ganan_calvo_map.png}
        \caption{Domains of existence (stability) of Taylor Cone Jets. \cite{gananCalvo} . The window formed by these points is where the system operated in the stable cone-jet. Operational windows depend of the liquid and configuration setup. Different windows are represented for different liquid conductivity. The X and Y axis are non-dimensional representation of electric potential and liquid flow rate, respectively.}
        \label{fig:ganan_calvo_fig}
    \end{figure}

@@

    In Figure \ref{fig:map2Data_fig} we can see the data acquired in this mapping experiments. The liquid used is pure ethanol. 
    Note that the experiment is composed of loops that increase voltage, change flowrate and repeat.

    \begin{figure}[H]
        \center
        \includegraphics[width=15cm]{Figuras/report2/map2Data.png}
        \caption{Mapping Experiment data collected. The figure has 3 graphs with shared x axis representing the samples collected. The first is the current values collected through all the experiment.
        The second is the voltage values applied in each window of data collected. The colors represent the spraying classification defined by our routine.
        The third graph shows the current mean value of each data sample.}
        \label{fig:map2Data_fig}
    \end{figure}

    With all the data collected, classified and saved in real time, we can do further analysis and studies. For example, Figure \ref{fig:map3Data_fig} illustrate the data classified by our algorithm and displayed in a Voltage X FlowRate range of spraying modes with a specific liquid setup so that we can compare the automatic results with previous researchs, such as showed in figure \ref{fig:ganan_calvo_fig} and validate the algorithm.

    \begin{figure}[H]
        \center
        \includegraphics[width=15cm]{Figuras/report4/map-2023-03-02.png}
        \caption{Mapping Experiment for pure ethanol in ambient conditions with our capilary setup. The map shows the stability region of each electrospraying mode in the voltage and flowrate range.}
        \label{fig:map3Data_fig}
    \end{figure}

### 2023-04-12 Documentation/UFMG/PFCII/Results/Results.tex
documentation

@@

    \begin{figure}[H]
        \center
        \includegraphics[width=12cm]{Figuras/report3/exp26-01-2.png}
        \caption{ exp-26-01-2 (V x Q)}
    \end{figure}

@@

        The Figure 13 shows a printscreen of how the experiment looks like in real time.
        We can see the image generated by the camera in the back.
        The routine code running in pycharm software on the right.
        And also real time signal plottings of the current data on the left.

        \begin{figure}[H]
            \center
            \includegraphics[width=17cm]{Figuras/19:03/axs1.png}
            \caption{running experiment print screen}
        \end{figure}

@@

@@

\section{Atividades do Projeto}
\label{sec:metodo3}

\section {Requisitos do Sistema}
\label{sec:req}

>>>>

\begin{figure}[H]
    \center
    \includegraphics[width=17cm]{Figuras/19:03/axs1.png}
    \caption{Printscreen of the window shows user interface during the experiment.
        We can see the image generated by the camera in the background.
        The routine code running in pycharm software on the right side.
        And also real time signal plottings of the current data on the left side.}
\end{figure}

@@

@@

@@

        To compare with the literature and validate the algorithm we decided to display the data using the non-dimensional numbers used in figure \ref{fig:ganan_calvo_fig}.

@@

### 2023-04-12 Documentation/UFMG/relatorios/Relatorio_4/Development/Development.tex
documentation

>>>>

As we can see in Figure 4 the plotting thread can simply be deactivated by a command in the configuration file.
With that we are capable of running the routine in a raspberry pi with python3 installed.
The raspberry pi offers the portable solution for the routine to be running and can be implemented in size constrained industries applications.
The raspberry pi is also integrated with a GSM data module to connect in internet through cellphone network.
